Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-02-06 vesicle_code/docs/adhesion/adhesion.tex
figures changed by yny

In this work we focus on weakly adhesive vesicles whose equilibrium
shapes in a quiescent flow are shown in the left plot of
Figure~\ref{fig:Dec18_vesicle_shape} for three reduced areas: $\Delta
A=0.95$, $0.75$, and $0.6$ with $\mathcal{H}=5$ and $\delta = 0.2$. 
\begin{figure}
  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_00.jpeg}
  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_01.jpeg}
  \caption{\label{fig:Dec18_vesicle_shape} Two vesicles of length $\pi$
  with $\kappa=1$, $\mathcal{H}=5$, and $\delta=0.2$.  {\em Left}:
  Equilibrium shapes of two vesicles under adhesive interactions with
  adhesion strength $\mathcal{H}=0.5$ and separation distance
  $\delta=0.2$.  Vesicle reduced area $\Delta A=0.95$, $0.75$, and $0.6$
  are labeled.  The color coding is the tension along the vesicle. {\em
  Right}: Membrane shapes in the contact region.} \todo[inline]{This
  caption contradicts itself.  Is it $\mathcal{H} = 0.5$ or $\mathcal{H}
  = 5$?}
\end{figure}
The equilibrium vesicle shape for $\Delta A=0.95$ is the circular cap
with a flat contact region.  This is similar to the observed shapes of
two vesicles under strong adhesive interaction
in~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.  When
vesicles are more deflated with a reduced area $\Delta A = 0.75$, the
equilibrium vesicle shape is elongated with a bigger contact region.
This is consistent with the equilibrium shapes of a vesicle doublet
under a L-J potential ($(m,n) =
(12,6)$)~\cite{FlormannAouane2017_SciReports}.  As the reduced area
decreases further, we observe undulation of the elongated equilibrium
vesicle shape on the non-contact side while the contact region remains
flat.  The color coding along each curve is the tension of the vesicle
membrane.  We observe that the membrane tension in the contact region is
very negative, indicating a dominant compression of membrane when the
adhesion force is strong to keep the vesicles bound together.

>>>>

In this work we focus on weakly adhesive vesicles whose equilibrium
shapes in a quiescent flow are shown in the left plot of
Figure~\ref{fig:Dec18_vesicle_shape} for three reduced areas: $\Delta
A=0.95$, $0.75$, and $0.6$ with $\mathcal{H}=5$ and $\delta = 0.2$. 
\begin{figure}
  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_00.jpeg}
  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_01.jpeg}
  \caption{\label{fig:Dec18_vesicle_shape} Two vesicles of length $\pi$
  with $\kappa=1$, $\mathcal{H}=5$, and $\delta=0.2$.  {\em Left}:
  Equilibrium shapes of two vesicles under adhesive interactions with
  adhesion strength $\mathcal{H}=5$ and separation distance
  $\delta=0.2$.  Vesicle reduced area $\Delta A=0.95$, $0.75$, and $0.6$
  are labeled.  The color coding is the tension along the vesicle. {\em
  Right}: Membrane shapes in the contact region.} \todo[inline]{This
  caption contradicts itself.  Is it $\mathcal{H} = 0.5$ or $\mathcal{H}
  = 5$?}
\end{figure}
The equilibrium vesicle shape for $\Delta A=0.95$ is the circular cap
with a flat contact region.  This is similar to the observed shapes of
two vesicles under strong adhesive interaction
in~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.  When
vesicles are more deflated with a reduced area $\Delta A = 0.75$, the
equilibrium vesicle shape is elongated with a bigger contact region.
This is consistent with the equilibrium shapes of a vesicle doublet
under a L-J potential ($(m,n) =
(12,6)$)~\cite{FlormannAouane2017_SciReports}.  As the reduced area
decreases further, we observe undulation of the elongated equilibrium
vesicle shape on the non-contact side while the contact region remains
flat.  The color coding along each curve is the tension of the vesicle
membrane.  We observe that the membrane tension in the contact region is
very negative, indicating a dominant compression of membrane when the
adhesion force is strong to keep the vesicles bound together.
